### 2023-09-23 chapters/paper_review/03_approaches.tex
Work on variational autoencoders

\edit{The Gumbel softmax \cite{jang_categorical_2017} is another frequently used approach for obtaining a discrete representation space, and has also been used for AEs \cite{eloff_unsupervised_2019}. In addition to the approaches discussed above, several other works on speech representation learning take inspiration from the AE framework \cite{zeiler_rectified_2013, badino_autoencoder_2014, badino_discovering_2015, kamper_unsupervised_2015, renshaw_comparison_2015, settle_acoustically_2019}.}

@@

\paragraph{wav2vec 2.0} 
\edit{The wav2vec 2.0 model combines contrastive learning with masking}. As the CPC model, it uses the InfoNCE loss \cite{oord_representation_2018} to maximize the similarity between a contextualized representation and a localized representation. \edit{However, instead of using the $z_t$ directly as positive and negatives, it uses a quantization module $g(\cdot)$ to obtain a discrete representation. This has the practical implication that one can avoid sampling negatives from the same category as the positive}. \edit{The model} takes as input a waveform and uses a convolutional module \edit{$f_1(\cdot)$} followed by a \edit{Transformer encoder} \edit{$f_2(\cdot)$}. Masking is applied to the output of the convolutional module: 
\begin{align}
    z_t &= f_1(X_{[t-u,t+u]}) \label{w2v2 f_v} \enspace , \\
    H &= f_2(m(Z)) \label{w2v2 f_c} \enspace , \\
    q_t &= g(z_t) \enspace . \label{w2v2 qtz}
\end{align}
\noindent
The quantization module $g(\cdot)$ uses a Gumbel softmax~\cite{jang_categorical_2017} with a straight-through estimator. Since the quality of the learned representations is contingent on the quality of the quantization, wav2vec 2.0 combines two techniques to learn high-quality codebooks. First, wav2vec 2.0 concatenates quantized representations from multiple codebooks at each timestep, so-called Product Quantization (PQ)~\cite{jegou_product_2011}. Also, the \edit{primary} training loss \edit{described below} is augmented with an auxiliary term designed to encourage equal use of all codebook entries.

@@

Several lines of work have begun to address the problem of learning representations of spans of speech, especially word segments, typically referred to as \textit{acoustic word embeddings}.  Early work on unsupervised acoustic word embeddings defined them as vectors of distances from the target segment to a number of pre-defined ``template" segments~\cite{levin_fixed-dimensional_2013}. Later work used variants of neural autoencoders~\cite{chung_audio_2016,holzenberger_learning_2018,kamper_truly_2019,peng_correspondence_2020}. These are often evaluated on word discrimination, that is the task of determining whether two word segments correspond to the same word or not~\cite{carlin_rapid_2011}. This task can be thought of as a proxy for query-by-example search, since the basic operation in search is to determine whether a segment in the search database matches a query segment, and has been used for evaluation of both frame-level (e.g.,~\cite{kamper_unsupervised_2015}) and word-level~\cite{levin_fixed-dimensional_2013,kamper_deep_2016} representations.

>>>>

\edit{The Gumbel softmax \cite{jang_categorical_2016} is another frequently used approach for obtaining a discrete representation space, and has also been used for AEs \cite{eloff_unsupervised_2019}. In addition to the approaches discussed above, several other works on speech representation learning take inspiration from the AE framework \cite{zeiler_rectified_2013, badino_autoencoder_2014, badino_discovering_2015, kamper_unsupervised_2015, renshaw_comparison_2015, settle_acoustically_2019}.}

@@

\paragraph{wav2vec 2.0} 
\edit{The wav2vec 2.0 model combines contrastive learning with masking}. As the CPC model, it uses the InfoNCE loss \cite{oord_representation_2018} to maximize the similarity between a contextualized representation and a localized representation. \edit{However, instead of using the $z_t$ directly as positive and negatives, it uses a quantization module $g(\cdot)$ to obtain a discrete representation. This has the practical implication that one can avoid sampling negatives from the same category as the positive}. \edit{The model} takes as input a waveform and uses a convolutional module \edit{$f_1(\cdot)$} followed by a \edit{Transformer encoder} \edit{$f_2(\cdot)$}. Masking is applied to the output of the convolutional module: 
\begin{align}
    z_t &= f_1(X_{[t-u,t+u]}) \label{w2v2 f_v} \enspace , \\
    H &= f_2(m(Z)) \label{w2v2 f_c} \enspace , \\
    q_t &= g(z_t) \enspace . \label{w2v2 qtz}
\end{align}
\noindent
The quantization module $g(\cdot)$ uses a Gumbel softmax~\cite{jang_categorical_2016} with a straight-through estimator. Since the quality of the learned representations is contingent on the quality of the quantization, wav2vec 2.0 combines two techniques to learn high-quality codebooks. First, wav2vec 2.0 concatenates quantized representations from multiple codebooks at each timestep, so-called Product Quantization (PQ)~\cite{jegou_product_2011}. Also, the \edit{primary} training loss \edit{described below} is augmented with an auxiliary term designed to encourage equal use of all codebook entries.

@@

Several lines of work have begun to address the problem of learning representations of spans of speech, especially word segments, typically referred to as \textit{acoustic word embeddings}.  Early work on unsupervised acoustic word embeddings defined them as vectors of distances from the target segment to a number of pre-defined ``template" segments~\cite{levin_fixeddimensional_2013}. Later work used variants of neural autoencoders~\cite{chung_audio_2016,holzenberger_learning_2018,kamper_truly_2019,peng_correspondence_2020}. These are often evaluated on word discrimination, that is the task of determining whether two word segments correspond to the same word or not~\cite{carlin_rapid_2011}. This task can be thought of as a proxy for query-by-example search, since the basic operation in search is to determine whether a segment in the search database matches a query segment, and has been used for evaluation of both frame-level (e.g.,~\cite{kamper_unsupervised_2015}) and word-level~\cite{levin_fixeddimensional_2013,kamper_deep_2016} representations.
